One-at-a-time Parameter Perturbation Ensemble of the Community Land Model, version 5.1

### 2025-03-31 ms/ms.tex
submission version

\begin{landscape}
 \begin{table}[h]
 \caption{In total, 211 parameters were perturbed in this experiment. These are the parameters mentioned within the main text. A complete set of parameters is included in a spreadsheet in the supplementary information.}
 \centering
 \begin{tabular}{l l c}
 \hline
  Parameter  & Description & Model Domain \\
 \hline
cv & Turbulent transfer coefficient & Sensible, latent heat and momentum fluxes \\
dleaf & Leaf characteristic length & Sensible, latent heat and momentum fluxes \\
d\_max & Dry surface layer (DSL) parameter & Sensible, latent heat and momentum fluxes \\
frac\_sat\_soil\_dsl\_init & Fraction of saturated soil at which DSL initiates & Sensible, latent heat and momentum fluxes \\
fff & Decay factor for fractional saturated area & Hydrology \\
liq\_canopy\_storage\_scalar & Canopy-storage-of-liquid-water parameter & Hydrology \\
maximum\_leaf\_wetted\_fraction & Maximum leaf wetted fraction & Hydrology \\
sand\_pf & Perturbation factor for sand content of soil column & Hydrology \\
sucsat\_sf & Scale factor for minimum soil water potential & Hydrology \\
medlynintercept & Medlyn intercept of conductance-photosynthesis relationship & Stomatal resistance and photosynthesis \\
medlynslope & Medlyn slope of conductance-photosynthesis relationship & Stomatal resistance and photosynthesis \\
tpu25ratio & Ratio of tpu25top to vcmax25top & Stomatal resistance and photosynthesis \\
jmaxb0 & Baseline proportion of nitrogen allocated for electron transport & Photosynthetic capacity\\
jmaxb1 & Response of electron transport rate to light & Photosynthetic capacity\\
slatop & Specific leaf area at top of canopy & Photosynthetic capacity\\
theta\_cj & empirical curvature parameter for photosynthesis colimitation& Photosynthetic capacity \\
wc2wjb0 & Baseline ratio of wc:wj & Photosynthetic capacity \\
FUN\_fracfixers & fraction of carbon available for N fixation & Fixation and uptake of Nitrogen \\
KCN & Nitrogen acquisition parameter group & Fixation and uptake of Nitrogen \\
kmax & Plant segment max conductance & Plant hydraulics \\
krmax & Root segment max conductance & Plant hydraulics \\
psi50 & Water potential at 50\% loss of conductance & Plant hydraulics \\
nstem & Stem number & Biomass heat storage \\
lmr\_intercept\_atkin & Intercept in the calculation of leaf maintenance respiration& Plant respiration \\
froot\_leaf & Allocation parameter: new fine root C per new leaf C & Carbon and nitrogen allocation \\
leafcn & Leaf C:N & Carbon and nitrogen allocation \\
leaf\_long & Leaf longevity & Vegetation phenology and turnover \\
cpha & Activation energy for cp & Acclimation parameters \\
jmaxhd & Deactivation energy for jmax & Acclimation parameters \\
kcha & Activation energy for kc & Acclimation parameters \\
lmrha & Activation energy for lmr & Acclimation parameters \\
lmrhd & Deactivation energy for lmr & Acclimation parameters \\
tpuha & Activation energy for tpu & Acclimation parameters \\
tpuse\_sf & Scale factor for tpu entropy term & Acclimation parameters \\
vcmaxha & Activation energy for vcmax & Acclimation parameters \\
vcmaxhd & Deactivation energy for vcmax & Acclimation parameters \\
 \hline
 \end{tabular}
 \end{table}
\end{landscape}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/main/deltas.png}
\caption{The eight most influential parameters on NEP (top row) in the control simulations (a), high CO$_2$ simulations (b), and the relative response to high CO$_2$ (c), as well as on evapotranspiration (ET, bottom row) in the control simulations (d), future climate simulations (e) and the relative response to future climate (f). The parameters that are most influential on present-day climate (a,d) can differ significantly from the parameters that control the response to forcing perturbations (c,f).}
\label{fig:nep}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/lai_biome.pdf}
\caption{The eight most influential parameters on leaf area index (LAI) within the control ensemble, globally and within three biomes. The solid lines span the range between the two simulations for each parameter, with an open circle indicating the simulation where a parameter is set to its minimum value and a filled circle for its maximum. The lines are color-coded according to scientific domain. The dashed lines indicate the LAI for the simulation with default CLM5.1 parameters. Parameter rankings vary by biome, with the global rankings seeming to reflect contributions from each of these three biomes.}
\label{fig:lai}
\end{figure}

>>>>

\begin{landscape}
 \begin{table}[h]
 \caption{In total, 211 parameters were perturbed in this experiment. These are the parameters mentioned within the main text. A complete set of parameters, with ranges, is included in a spreadsheet in the supplementary information.}
 \centering
 \begin{tabular}{l l c}
 \hline
  Parameter  & Description & Model Domain \\
 \hline
cv & Turbulent transfer coefficient & Sensible, latent heat and momentum fluxes \\
dleaf & Leaf characteristic length & Sensible, latent heat and momentum fluxes \\
d\_max & Dry surface layer (DSL) parameter & Sensible, latent heat and momentum fluxes \\
frac\_sat\_soil\_dsl\_init & Fraction of saturated soil at which DSL initiates & Sensible, latent heat and momentum fluxes \\
fff & Decay factor for fractional saturated area & Hydrology \\
liq\_canopy\_storage\_scalar & Canopy-storage-of-liquid-water parameter & Hydrology \\
maximum\_leaf\_wetted\_fraction & Maximum leaf wetted fraction & Hydrology \\
sand\_pf & Perturbation factor for sand content of soil column & Hydrology \\
sucsat\_sf & Scale factor for minimum soil water potential & Hydrology \\
medlynintercept & Medlyn intercept of conductance-photosynthesis relationship & Stomatal resistance and photosynthesis \\
medlynslope & Medlyn slope of conductance-photosynthesis relationship & Stomatal resistance and photosynthesis \\
tpu25ratio & Ratio of tpu25top to vcmax25top & Stomatal resistance and photosynthesis \\
jmaxb0 & Baseline proportion of nitrogen allocated for electron transport & Photosynthetic capacity\\
jmaxb1 & Response of electron transport rate to light & Photosynthetic capacity\\
slatop & Specific leaf area at top of canopy & Photosynthetic capacity\\
theta\_cj & empirical curvature parameter for photosynthesis colimitation& Photosynthetic capacity \\
wc2wjb0 & Baseline ratio of wc:wj & Photosynthetic capacity \\
FUN\_fracfixers & fraction of carbon available for N fixation & Fixation and uptake of Nitrogen \\
KCN & Nitrogen acquisition parameter group & Fixation and uptake of Nitrogen \\
kmax & Plant segment max conductance & Plant hydraulics \\
krmax & Root segment max conductance & Plant hydraulics \\
psi50 & Water potential at 50\% loss of conductance & Plant hydraulics \\
nstem & Stem number & Biomass heat storage \\
lmr\_intercept\_atkin & Intercept in the calculation of leaf maintenance respiration& Plant respiration \\
froot\_leaf & Allocation parameter: new fine root C per new leaf C & Carbon and nitrogen allocation \\
leafcn & Leaf C:N & Carbon and nitrogen allocation \\
leaf\_long & Leaf longevity & Vegetation phenology and turnover \\
cpha & Activation energy for cp & Acclimation parameters \\
jmaxhd & Deactivation energy for jmax & Acclimation parameters \\
kcha & Activation energy for kc & Acclimation parameters \\
lmrha & Activation energy for lmr & Acclimation parameters \\
lmrhd & Deactivation energy for lmr & Acclimation parameters \\
tpuha & Activation energy for tpu & Acclimation parameters \\
tpuse\_sf & Scale factor for tpu entropy term & Acclimation parameters \\
vcmaxha & Activation energy for vcmax & Acclimation parameters \\
vcmaxhd & Deactivation energy for vcmax & Acclimation parameters \\
 \hline
 \end{tabular}
 \end{table}
\end{landscape}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/main/deltas.png}
\caption{The eight most influential parameters \add{(ranked by absolute parameter effect)} on NEP (top row) in the control simulations (a), high CO$_2$ simulations (b), and the relative response to high CO$_2$ (c), as well as on evapotranspiration (ET, bottom row) in the control simulations (d), future climate simulations (e) and the relative response to future climate (f). The parameters that are most influential on present-day climate (a,d) can differ significantly from the parameters that control the response to forcing perturbations (c,f).}
\label{fig:nep}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/lai_biome.pdf}
\caption{The eight most influential parameters \add{(ranked by absolute parameter effect)} on leaf area index (LAI) within the control ensemble, globally and within three biomes. The solid lines span the range between the two simulations for each parameter, with an open circle indicating the simulation where a parameter is set to its minimum value and a filled circle for its maximum. The lines are color-coded according to scientific domain. The dashed lines indicate the LAI for the simulation with default CLM5.1 parameters. Parameter rankings vary by biome, with the global rankings seeming to reflect contributions from each of these three biomes.}
\label{fig:lai}
\end{figure}
